---
title: "AS3-1: 數位偵探"
author: "第 18 組"
date: "`r Sys.time()`"
output: 
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

```{r results='hide', message=FALSE, warning=FALSE, echo=F}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr, d3heatmap)
```
<hr>

犯罪是一個國際關注的問題，但它在不同的國家以不同的方式記錄和處理。 在美國，聯邦調查局（FBI）記錄了暴力犯罪和財產犯罪。 此外，每個城市都記錄了犯罪行為，一些城市發布了有關犯罪率的數據。 伊利諾伊州芝加哥市從2001年開始在線發布犯罪數據。

芝加哥是美國人口第三多的城市，人口超過270萬。在這個作業裡面，我們將關注一種特定類型的財產犯罪，稱為「汽車盜竊」，我們將使用R中的一些基本數據分析來了解芝加哥的汽車盜竊紀錄。請載入文件"data/mvtWeek1.csv"：以下是各欄位的描述：

+ `ID`: a unique identifier for each observation
+ `Date`: the date the crime occurred
+ `LocationDescription`: the location where the crime occurred
+ `Arrest`: whether or not an arrest was made for the crime (TRUE if an arrest was made, and FALSE if an arrest was not made)
+ `Domestic`: whether or not the crime was a domestic crime, meaning that it was committed against a family member (TRUE if it was domestic, and FALSE if it was not domestic)
+ `Beat`: the area, or "beat" in which the crime occurred. This is the smallest regional division defined by the Chicago police department.
+ `District`: the police district in which the crime occured. Each district is composed of many beats, and are defined by the Chicago Police Department.
+ `CommunityArea`: the community area in which the crime occurred. Since the 1920s, Chicago has been divided into what are called "community areas", of which there are now 77. The community areas were devised in an attempt to create socially homogeneous regions.
+ `Year`: the year in which the crime occurred.
+ `Latitude`: the latitude of the location at which the crime occurred.
+ `Longitude`: the longitude of the location at which the crime occurred.

<br>

- - -

###  Section-1 Loading the Data

【1.1】How many rows of data (observations) are in this dataset?
```{r}
#載入資料並命名為data1
data1=read.csv("data/mvtWeek1.csv",stringsAsFactors = F)
nrow(data1)
```

檢查各欄位的資料格式
```{r}
#摘要data1中的各欄位
summary(data1)
```

類別(Factor) versus 字串(Character)

【1.2】How many variables are in this dataset?
```{r}
#計算data1中有多少筆欄位
ncol(data1)
```


【1.3】Using the "max" function, what is the maximum value of the variable "ID"?
```{r}
#找出data1中ID中最大的的數
max(data1$ID)
```


【1.4】 What is the minimum value of the variable "Beat"?
```{r}
#找出data1中Beat中最小的數
min(data1$Beat)
```


【1.5】 How many observations have value TRUE in the Arrest variable (this is the number of crimes for which an arrest was made)?
```{r}
#計算data1中有多少筆犯罪有逮捕犯人歸案
sum(data1$Arrest)
```

【1.6】 How many observations have a LocationDescription value of ALLEY?
```{r}
#取data1中發生在巷子裡犯罪的平均數
mean(data1$LocationDescription == "ALLEY")
```


<br><br>

- - -

### Section-2 Understanding Dates in R

【2.1】 In what format are the entries in the variable Date?

+ Month/Day/Year Hour:Minute
+ Day/Month/Year Hour:Minute
+ Hour:Minute Month/Day/Year
+ Hour:Minute Day/Month/Year

```{r}
#列出data1中前幾筆資料
head(data1$Date)
```

```{r}
#將data1中字串轉日期，並以月日年小時分鐘的格式來排序
ts = as.POSIXct(data1$Date, format="%m/%d/%y %H:%M")
```

```{r}
#調整直方圖大小
par(cex=0.7)
```

```{r fig.height=2.5, fig.width=8}
#繪出直方圖，以las=2來控制座標的數字呈現方式為與軸垂直，以日期區間為x軸，頻率為y軸
hist(ts,"quarter",las=2,freq=T,xlab="")
```


【2.2】 What is the month and year of the median date in our dataset? 
```{r}
#找出時間的中位數
median(ts)
```

【2.3】 In which month did the fewest motor vehicle thefts occur?
```{r}
#以時間中的月份來分類，計算機車竊盜案件數量，再由小到大重新排序
sort(table(format(ts,"%m")))
```

【2.4】 On which weekday did the most motor vehicle thefts occur?
```{r}
#以時間中的星期幾來分類，計算機車竊盜案件數量，再由小到大重新排序
sort(table(format(ts,"%w")))
```

【2.5】 Which month has the largest number of motor vehicle thefts for which an arrest was made?
```{r}
#列出data1中所有機車竊盜被逮捕的時間，在歸類到是哪一月份，製成表格後再依小到大重新排序
ts[data1$Arrest] %>% format("%m") %>% table %>% sort
```

<br><br>

- - -

### Section-3 Visualizing Crime Trends

【3.1】 (a) In general, does it look like crime increases or decreases from 2002 - 2012? (b) In general, does it look like crime increases or decreases from 2005 - 2008? (c) In general, does it look like crime increases or decreases from 2009 - 2011?
```{r}
#以年為區間來計算犯罪數量的直方圖，以las=2來控制座標的數字呈現方式為與軸垂直
hist(ts,'year',las=2)
```

【3.2】 Does it look like there were more crimes for which arrests were made in the first half of the time period or the second half of the time period?
```{r}
#把字串轉成日期，2000年到2014年間，以2007年1月1日區分為上下半年，製成表格，以便找出哪一區間的犯罪數量較多
table(ts > as.POSIXct("2007-01-01"))
```

【3.3】 For what proportion of motor vehicle thefts in 2001 was an arrest made?
```{r}
##先分出年份，計算機車竊盜的案件數量，再換算成比例，並取到小數點後三位
table(data1$Arrest, format(ts,'%Y')) %>% prop.table(2) %>% round(3)
```

【3.4】 For what proportion of motor vehicle thefts in 2007 was an arrest made?
```{r}
##先分出年份，計算機車竊盜案件數量的平均數，再換算成比例，並取到小數點後三位
tapply(data1$Arrest, format(ts,'%Y'), mean) %>% round(3)
```

【3.5】 For what proportion of motor vehicle thefts in 2012 was an arrest made?
```{r}
#先分出年份，計算機車竊盜的案件數量，再換算成比例，並取到小數點後三位
table(data1$Arrest, format(ts,'%Y')) %>% prop.table(2) %>% round(3)
```

<br><br>

- - -

### Section-4 Popular Locations

【4.1】 Which locations are the top five locations for motor vehicle thefts, excluding the "Other" category? You should select 5 of the following options.

```{r}
#找出前五個最常發生機車竊盜的地點類別，其於的歸為其他，並以小到大重新排序，最後再列出最後六筆資料
table(data1$LocationDescription) %>% sort %>% tail(6)
```

【4.2】 How many observations are in Top5?
```{r}
#定義top5為前五個最常發生機車竊盜的地點類別，依小到大重新排序，總共有幾起案件
top5 = names(table(data1$LocationDescription) %>% sort %>% tail(6))[-4]
sum(data1$LocationDescription %in% top5)
```

【4.3】 One of the locations has a much higher arrest rate than the other locations. Which is it? 
```{r}
#篩選出在top5篩選犯罪地點，並在top5中的各犯罪地點，計算被逮捕犯人數量的平均數，再依小到大重新排序
TOP5 = subset(data1, LocationDescription %in% top5)
tapply(TOP5$Arrest, TOP5$LocationDescription, mean) %>% sort
```

【4.4】 On which day of the week do the most motor vehicle thefts at gas stations happen?
```{r}
#找出在加油站發生機車偷竊的案件的時間，並以星期幾來呈現，製成表格，再由小到大重新排列
ts[data1$Location == "GAS STATION"] %>% format('%w') %>% table %>% sort
```

【4.5】 On which day of the week do the fewest motor vehicle thefts in residential driveways happen?
```{r}
#找出住宅區的車道上發生機車偷竊的案件的時間，並以星期幾來呈現，製成表格，再由小到大重新排列
ts[data1$Location == "DRIVEWAY - RESIDENTIAL"] %>% format('%w') %>% table %>% sort
```


<br><br><br>


