---
title: "AS3-2: 股市動態"
author: "第 18 組"
date: "`r Sys.time()`"
output:
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr)
```
<hr>

**股票動態**

股票市場是買賣雙方交易公司股票的地方，也是個人和公司投資的最受歡迎的方式之一。現在估計世界股票市場規模達到數兆。紐約證券交易所位於紐約市，是世界上最大的股票市場。 紐約證券交易所約有2,800家上市公司。在這個問題上，我們將看看其中五家公司的每月股價：IB、通用電氣（GE）、寶潔、可口可樂和波音。此問題中使用的數據來自Infochimps。

使用`read.csv()`下載並讀取以下文件：

+ `data/IBMStock.csv`
+ `data/GEStock.csv`
+ `data/ProcterGambleStock.csv`
+ `data/CocaColaStock.csv`
+ `data/BoeingStock.csv` 

分別存入資料框`IBM`、`GE`、`ProcterGamble`、`CocaCola`和`Boeing`，
每個資料框都有兩個變量，描述如下：
```{r}
IBM = read.csv("data/IBMStock.csv")
GE = read.csv("data/GEStock.csv")
ProcterGamble = read.csv("data/ProcterGambleStock.csv")
CocaCola = read.csv("data/CocaColaStock.csv")
Boeing = read.csv("data/BoeingStock.csv")
```

+ `Date`：日期
+ `StockPrice`：給定月份公司的平均股價

在這個案例，我們將看看這些公司的股票動態如何隨著時間的推移而發生變化。

<br><hr>

###  Section-1 Summary Statistics

__§ 1.1__ Our five datasets all have the same number of observations. How many observations are there in each data set?
```{r}
nrow(IBM)
nrow(GE)
nrow(ProcterGamble)
nrow(CocaCola)
nrow(Boeing)
#480

```


__§ 1.2__ What is the earliest year in our datasets?
```{r}
combind <- rbind(IBM,GE,ProcterGamble,CocaCola,Boeing)
date = as.POSIXct(combind$Date, format="%m/%d/%y")
which.min(date)
date[1]
#1970
```

__§ 1.3__ What is the latest year in our datasets?
```{r}
which.max(date)
date[480]
#2009
```

__§ 1.4__ What is the mean stock price of IBM over this time period?
```{r}
mean(IBM$StockPrice)
#144.375
#
```

__§ 1.5__ What is the minimum stock price of General Electric (GE) over this time period?
```{r}
min(GE$StockPrice)
#9.293636
#
```

__§ 1.6__ What is the maximum stock price of Coca-Cola over this time period?
```{r}
max(CocaCola$StockPrice)
#146.5843
#
```

__§ 1.7__ What is the median stock price of Boeing over this time period?
```{r}
median(Boeing$StockPrice)
#44.8834
#
```

__§ 1.8__ What is the standard deviation of the stock price of Procter & Gamble over this time period?
```{r}
sd(ProcterGamble$StockPrice)
#18.19414
#
```

<br><hr>

###  Section-2 Visualizing Stock Dynamics

__§ 2.1__ Around what year did Coca-Cola has its highest stock price in this time period? Around what year did Coca-Cola has its lowest stock price in this time period?
```{r}
CocaCola$Date = as.POSIXct(CocaCola$Date, format="%m/%d/%y")
plot(CocaCola$Date, CocaCola$StockPrice, type="l")
points(x=CocaCola$Date[which.min(CocaCola$StockPrice)], 
       y=min(CocaCola$StockPrice), 
       pch=16,               # 點的圖形
       col="red")            # 顏色
#
#
```


__§ 2.2__ In March of 2000, the technology bubble burst, and a stock market crash occurred. According to this plot, which company's stock dropped more?
```{r}
plot(CocaCola$Date, CocaCola$StockPrice, type="l", col="red")
ProcterGamble$Date = as.POSIXct(ProcterGamble$Date, format="%m/%d/%y")
GE$Date = as.POSIXct(GE$Date, format="%m/%d/%y")
Boeing$Date = as.POSIXct(Boeing$Date, format="%m/%d/%y")
lines(ProcterGamble$Date, ProcterGamble$StockPrice, col="blue")
lines(IBM$Date, IBM$StockPrice, col = "orange")
lines(GE$Date, GE$StockPrice, col = "green")
lines(Boeing$Date, Boeing$StockPrice, col = "brown")
abline(v=as.POSIXct("2000-03-01"), lwd=1)
#
#
```

__§ 2.3__ (a) Around 1983, the stock for one of these companies (Coca-Cola or Procter and Gamble) was going up, while the other was going down. Which one was going up? 
```{r}
plot(CocaCola$Date, CocaCola$StockPrice, type="l", col="red")
lines(ProcterGamble$Date, ProcterGamble$StockPrice, col="blue")
abline(v=as.POSIXct("1983-01-01"), lwd=2)

#Coca-Cola is going up
#Procter and Gamble is going down
```

(b) In the time period shown in the plot, which stock generally has lower values?
```{r}
#Coca-Cola has lower price
#
```


<br><hr>

###  Section-3 Visualizing Stock Dynamics 1995-2005

__§ 3.1__ Which stock fell the most right after the technology bubble burst in March 2000?
```{r}
plot(CocaCola$Date[301:432], CocaCola$StockPrice[301:432], type="l", col="red", ylim=c(0,210))
lines(ProcterGamble$Date[301:432], ProcterGamble$StockPrice[301:432], col="blue")
lines(IBM$Date[301:432], IBM$StockPrice[301:432], col="orange")
lines(GE$Date[301:432], GE$StockPrice[301:432], col="brown")
lines(Boeing$Date[301:432], Boeing$StockPrice[301:432], col="green")
legend("topright",                                # 表示在右上角
       pch = 1,                                   # pch代表點的圖案
       col = c("red", "blue", "orange", "brown", "green"),  # col代表顏色 
       legend = c("Ccca", "Procter", "IBM", "GE", "Boeing") # 顏色所對應的名稱
       )
abline(v=as.POSIXct("2000-03-01"), lwd=1)
#Boeing
#
```

__§ 3.2__ Which stock reaches the highest value in the time period 1995-2005?
```{r}
#IBM
#
```

__§ 3.3__ In October of 1997, there was a global stock market crash that was caused by an economic crisis in Asia. Comparing September 1997 to November 1997, which companies saw a decreasing trend in their stock price? (Select all that apply.)
```{r}
plot(CocaCola$Date[301:432], CocaCola$StockPrice[301:432], type="l", col="red", ylim=c(0,210))
lines(ProcterGamble$Date[301:432], ProcterGamble$StockPrice[301:432], col="blue")
lines(IBM$Date[301:432], IBM$StockPrice[301:432], col="orange")
lines(GE$Date[301:432], GE$StockPrice[301:432], col="brown")
lines(Boeing$Date[301:432], Boeing$StockPrice[301:432], col="green")
legend("topright",                                # 表示在右上角
       pch = 1,                                   # pch代表點的圖案
       col = c("red", "blue", "orange", "brown", "green"),  # col代表顏色 
       legend = c("Ccca", "Procter", "IBM", "GE", "Boeing") # 顏色所對應的名稱
       )
abline(v=as.POSIXct("1997-09-01"), lwd=2)
abline(v=as.POSIXct("1997-11-01"), lwd=2)
#Procter and Boeing
#
```

__§ 3.4__ In the last two years of this time period (2004 and 2005) which stock seems to be performing the best, in terms of increasing stock price?
```{r}
plot(CocaCola$Date[301:432], CocaCola$StockPrice[301:432], type="l", col="red", ylim=c(0,210))
lines(ProcterGamble$Date[301:432], ProcterGamble$StockPrice[301:432], col="blue")
lines(IBM$Date[301:432], IBM$StockPrice[301:432], col="orange")
lines(GE$Date[301:432], GE$StockPrice[301:432], col="brown")
lines(Boeing$Date[301:432], Boeing$StockPrice[301:432], col="green")
legend("topright",                                # 表示在右上角
       pch = 1,                                   # pch代表點的圖案
       col = c("red", "blue", "orange", "brown", "green"),  # col代表顏色 
       legend = c("Ccca", "Procter", "IBM", "GE", "Boeing") # 顏色所對應的名稱
       )
abline(v=as.POSIXct("2004-01-01"), lwd=2)
abline(v=as.POSIXct("2005-12-31"), lwd=2)
#Boeing
#
```


<br><hr>


###  Section-4 Monthly Trends

__§ 4.1__ For IBM, compare the monthly averages to the overall average stock price. In which months has IBM historically had a higher stock price (on average)? Select all that apply.
```{r}
IBM$Date = as.POSIXct(IBM$Date, format="%m/%d/%y")
sort(tapply(IBM$StockPrice, months(IBM$Date), mean))
mean(IBM$StockPrice)
#January - May's average price are higher than overall average price

```

__§ 4.2__ General Electric and Coca-Cola both have their highest average stock price in the same month. Which month is this?
```{r}
GE$Date = as.POSIXct(GE$Date, format="%m/%d/%y")
sort(tapply(GE$StockPrice, format(GE$Date,"%m"), mean))
CocaCola$Date = as.POSIXct(CocaCola$Date, format="%m/%d/%y")
sort(tapply(CocaCola$StockPrice, format(CocaCola$Date,"%m"), mean))
#Coca : april
#GE: march
```

__§ 4.3__ For the months of December and January, every company's average stock is higher in one month and lower in the other. In which month are the stock prices lower?
```{r}
tapply(IBM$StockPrice, format(IBM$Date,"%m"), mean)
#Dec is lower

```

<br><br><br>

